# (PART\*) COMMUNITY ANALYSIS AND FEEDBACK {-}

<!-- Set up code -->
```{r, include = FALSE}
ottrpal::set_knitr_image_path()
```

# Scientific Posters

In this section we will go over how to create a scientific poster. We chose a poster as our final deliverable in C-MOOR because they:


- **Facilitate participation in research symposiums**: Students can use their poster to apply to present at research symposiums or conferences with minimal additional effort beyond what they do in class. If your institution does not have a research day, consider starting one using these posters as a foundation as we did at Clovis Community College! Your school's library is another great point of contact in getting a poster session or research day set up. Some of the events students have participated in using their C-MOOR projects include:

  - The Clovis Community College Research Day
  - The Notre Dame of Maryland University Research Day
  - The GRADS-4C Conference (2025)

<!-- Why is it not making a space? -->


- **Serve as a physical representation of student achievement**: If printed, once finished with the class, students can choose to take their poster with them or leave it with the class to be hung up around the classroom or the hallways. This gives their research project more visibility, serves as an advertisement for other students who might be interested in taking the class, and showcases what students have accomplished. 

<!-- # ```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Image test"} -->
<!-- #  -->
<!-- # ottrpal::include_slide("https://docs.google.com/presentation/d/1dI8-_iVqbkzNMf11M4dK85E8ZW3OyZECs_YwMKw5fhs/edit?slide=id.g362974128df_0_0") -->
<!-- #  -->
<!-- #  -->
<!-- # ``` -->

- **Can easily be shared digitally**: A presentation can't be repeated twice without a recording, and each recording can take up a lot of digital storage. A poster on the other hand, is a great compressed product that can be posted on a student's (or the institution's) social media and help get their work seen by others. Posters are even small enough that they can be attached to an email and sent to prospective supervisors and collaborators interested in a quick summary of their work. See our [Look at This!](https://help.c-moor.org/c/look-at-this/) category on the C-MOOR Academy Discussion Forum to see all the posters students have created and shared so far!

- **Posters can be used to measure student achievement and understanding**: We have previously used these posters to evaluate student learning, even years after students have left the classroom. Check out our [poster on posters!](https://drive.google.com/file/d/1kK6FBBLbHiAAsTUgxwzHRlK1qCo__eCy/view?usp=sharing)


## Lecture - Scientific Posters

*Estimated time: ---*

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Image test"}

ottrpal::include_slide("https://docs.google.com/presentation/d/1dI8-_iVqbkzNMf11M4dK85E8ZW3OyZECs_YwMKw5fhs/edit#slide=id.g362823fe47a_0_72")

```


[Scientific Posters](https://docs.google.com/presentation/d/1-orSi8DpN22hMt9-6p_rHZnte1YXXLe-a132HDSyd0U/edit?usp=sharing)

## Activity - Scientific Posters

### Activity

*Estimated time: ---*

#### Instructions

1. Review **[Presentations Guidelines for Posters](https://ur.umbc.edu/urcad/resources/posters-guidelines)**

2. Skim three posters from among the following (must be Biology if from UMBC Posters)

- **[Look at This! Category on the Academy Discussion Forum](https://help.c-moor.org/c/look-at-this/8)**

- **[UMBC Biology Posters](https://ur.umbc.edu/poster-presentation-examples)**

- **[The example PacBio Poster](https://www.pacb.com/wp-content/uploads/PAG-Portik.pdf)**

3. Pick one poster and address the following points.

- **Notice** – What about this poster most interests you?

- **Wonder** – Two or three questions you would ask the authors.

- **Support** – Two or three suggestions on how the poster could be improved.

4. Post your answers by replying to the “Project Work: Scientific Posters” topic in the Discussion Forum

### Grading Criteria

- <mark style="background-color: yellow">Submit URL to your reply on Canvas

### Footnotes

**Contributions and Affiliations**

- Valeriya Gaysinskaya, Johns Hopkins University
- Frederick Tan, Johns Hopkins University

Last Revised: February 2025


## Group Poster 

### Preparing to make a poster

An important part of scientific research is presenting your findings. This might be in the form of a peer-reviewed journal article or a more informal poster presentation at a conference or symposium. In this assignment, students will work with their groups to put together their work from the C-MOOR Labs into a research poster.

Although the same information is in a poster, presentation, and a paper, each format requires a vastly different approach!

Here's an example of a [poster](https://drive.google.com/file/d/13EHQmlryoGs9yqTuOmGgU1064D2q937L/view?usp=sharing), [a presentation](https://drive.google.com/file/d/1gtkCgwE1Q_zM0IkrnJxfdYF2U8v15J_2/view?usp=sharing), and a [paper](https://drive.google.com/file/d/1f9akqYSxq4CO3w3pehEmG0TVzMicsOVc/view?usp=sharing) all from the same study. 

Notice how they all contain different levels of detail, different numbers of figures, and use language aimed for a specific audience. Your poster should look distinct from your presentation or paper.

### Part 1 - Choose a Template

*Estimated time: 5 minutes*

1. With your group, open a suggested [poster template](https://docs.google.com/presentation/d/1chz02nzYklAEjOtHrPsJZccGy1sFUZvqdlfcUyfj3I4/edit?usp=sharing) to use for your poster. 
1. Discuss with your group how you will divide up the work and exchange important information (e.g. phone numbers, email). Consider the following sections: 

- Abstract 
- Introduction
- Methods
- Results
- Discussion
- References 
- Acknowledgments

Notice these posters are sized at 36 x 42 inches, but there are many other commonly used sizes. Refer to your instructor on what poster size to use; not every poster will fit every stand when printed (if applicable). Notice that the posters in this slidedeck come in two-column, three-column, and mixed formats. Think about your figures and tables and select a format that makes the most sense for them. There are also some example posters in the last two slides that we will use to examine the anatomy of a research poster further in the next part.


### Part 2 - Make an Academic Research Poster

*Estimated time: ---*

1. Complete the following components of your research poster with your group. You might not do them in this order, but these are the components you are being graded on. For more details on each of these sections and their role in a scientific paper, see the Scientific Literature Lab.

#### The header: title, authors, and affiliations

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Image test"}

ottrpal::include_slide("https://docs.google.com/presentation/d/1dI8-_iVqbkzNMf11M4dK85E8ZW3OyZECs_YwMKw5fhs/edit#slide=id.g362974128df_0_11")

```

Since you completed this work as a team of scientists, all of your team members are considered authors. List your team members in alphabetical order. The author’s affiliation is the university, college, research institution or company that the work was conducted at.  An example affiliation for Clovis Community College would be: “Department of Biology, Clovis Community College, California, United States.” If multiple institutions exist, you will need to use superscript to denote who has what affiliation (see the example poster).

We will include the C-MOOR logo, the logo of your institution(s), and the most immediately relevant funding source (if applicable) in the header.

<!-- NOTE: &nbsp; creates a space in Markdown. In this instance, adding extra spaces after the checkbox didn't seem to work. -->

**Check the header of your poster:**

- [ ] &nbsp;All authors are listed
- [ ] &nbsp;The affiliations of all authors are listed
- [ ] &nbsp;The C-MOOR logo is included
- [ ] &nbsp;The logos of your institutions are included

- [ ] &nbsp;The title of the poster is focused on your specific project topic (ex. genes, variables, model organism)
- [ ] &nbsp;The title of the poster describes the main result of your research
- [ ] &nbsp;The title of the poster does not overstate the findings or significance of your research



#### Abstract

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Image test"}

ottrpal::include_slide("https://docs.google.com/presentation/d/1dI8-_iVqbkzNMf11M4dK85E8ZW3OyZECs_YwMKw5fhs/edit#slide=id.g362974128df_0_18")

```

An abstract is a concise summary of your paper. An effective abstract will inform the reader of the scientific hypothesis being tested, the purpose of the study, the main methods, and the most important results and conclusions. You may notice that not all posters online contain and abstract; different fields of science have slightly different requirements and formats for abstracts. 

**Your abstract should do the following:**

- [ ] &nbsp;1 sentence on why your research matters
- [ ] &nbsp;1 sentence summarizing your methodology
- [ ] &nbsp;1-2 sentence with the main results without interpretation (ex. we found that gene X was differentially abundant between the eye and all other tissues; we found an association between age and the presence of Y bacteria)
- [ ] &nbsp;1 sentence on what new knowledge you have contributed from your research (ex. gene X plays a key role in the eye, Y bacteria which is associated with function Z is associated with older populations)
- [ ] &nbsp;The abstract is no longer than 200 words; no unnecessary words are included

#### Introduction

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Image test"}

ottrpal::include_slide("https://docs.google.com/presentation/d/1dI8-_iVqbkzNMf11M4dK85E8ZW3OyZECs_YwMKw5fhs/edit#slide=id.g362974128df_0_21")

```


A good introduction section should do two things. First, it provides context for your work by describing what is already known in the field, as well as an unknown that your research is addressing. The latter is often called the gap in knowledge. Second, it should identify your scientific question and hypothesis. Usually, the introduction starts broadly, describing the work of other scientists. It is important to summarize this work (do not quote) and to properly cite the work.

When writing your introduction, it is often helpful to start at the end. Identify your scientific question, your hypothesis and the gap of knowledge first. Then brainstorm what you will need to tell your readers in terms of context and background. 

**Check your poster's introduction:**


The introduction contains:

- [ ] &nbsp;Why your research is novel
- [ ] &nbsp;Why your research matters (ex. any relevant disease states)
- [ ] &nbsp;The aim and/or hypotheses of your research
- [ ] &nbsp;Information on why the model organism used is a good model (if relevant to your project)

Check that:

- [ ] &nbsp;The introduction is brief (ex. no more than 200 words)
- [ ] &nbsp;The introduction is formatted in bullet points, not paragraphs
- [ ] &nbsp;All statements that require references have an in-line reference

#### Materials and Methods

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Image test"}

ottrpal::include_slide("https://docs.google.com/presentation/d/1dI8-_iVqbkzNMf11M4dK85E8ZW3OyZECs_YwMKw5fhs/edit#slide=id.g362974128df_0_27")

```
The materials and methods section will detail your analysis of the data. Don’t provide any of your results, just the methods. If you did not generate the data yourself from raw samples, you will simply cite the paper that made them instead of detailing their construction. We will also need to list any programs we used and provide credit to their creators.

Some other things you might include would be what type of analysis you decided to do (which parts of the body parts you analyzed, sets of genes, what p-value you used, etc.).

**Check your poster's materials and methods section:**

- [ ] &nbsp;You have listed the source of your data (ex. the published study your data came from) and added the appropriate in-line citation
- [ ] &nbsp;You have listed all R packages and/or websites you used (ex. DESeq2, ClustrProfiler, Phyloseq, FlyBase, Human Protein Atlas, CellxGene) and added the appropriate in-line citation
- [ ] &nbsp;You list what p-value you tested for significance at (usually 0.05)
- [ ] &nbsp;Another student from your class would be able to replicate your research based on what you wrote


#### Results
```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Image test"}

ottrpal::include_slide("https://docs.google.com/presentation/d/1dI8-_iVqbkzNMf11M4dK85E8ZW3OyZECs_YwMKw5fhs/edit#slide=id.g362974128df_0_24")

```
The Results section is where you will detail your data primarily through figures and tables, though sometimes written text is included. Begin by creating your tables and figures. Place the figures and tables in order of how you want to present them and name them such as Figure 1, Figure 2, Table 1, Table 2, etc. 

Every figure and table must have a legend that goes with it in a smaller font.
Figures have their legends *underneath* them. Tables have their figures *above* them.
These legends should be in a smaller font than the rest of the text on the poster. 
Each legend begins with 1 sentence summarizing the takeaway idea from the figure/table. If necessary, add 1-2 sentences of detail on the context and/or methodology used to generate the figure or table to give context to the audience on what they are looking at.

If you are including written text of your results, you should go through each figure in order, emphasizing any important results from each one. As you discuss each figure, you will reference the figure or table in parentheses. For example: “RT-PCR analysis shows an increase in gene expression for gene X (Fig 2).” 

Have fun playing around with how to organize your figures with the text to make the poster look professional. You need a minimum of 2 figures for your poster.

**Check your poster's results section:**

- [ ] &nbsp;You have a minimum of 2 figures on the poster
- [ ] &nbsp;All figures have a labeled x and y-axis
- [ ] &nbsp;All figures have a legend underneath them
- [ ] &nbsp;All tables have a legend above them
- [ ] &nbsp;The legends have 1 sentence summarizing the figure or table's main idea
- [ ] &nbsp;If necessary, the legends have 1-2 sentences detailing the methodology and or other context of the figure/table

#### Discussion

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Image test"}

ottrpal::include_slide("https://docs.google.com/presentation/d/1dI8-_iVqbkzNMf11M4dK85E8ZW3OyZECs_YwMKw5fhs/edit#slide=id.g362974128df_0_52")

```

The discussion section of the paper is your chance to analyze and interpret your results. For your lab report, make sure your discussion section includes all of the following:

- What do your results mean?
- How do they fit into the bigger picture?
- If any experiments did not give expected results, hypothesize why that might have been the case and propose alternate experiments that could confirm or clarify your results.
- Include at least one sentence of future work that you would do if you had more time or what students in upcoming semesters could do to continue to answer your questions.

**Check your poster's discussion section:**

- [ ] &nbsp;1 sentence for each major result that relates to your hypothesis
- [ ] &nbsp;1-2 sentences how these results matter based on the problem you described in your introduction
- [ ] &nbsp;1 sentence describing future work someone else could do as a logical next step in addressing the problem you described in your introduction
- [ ] &nbsp;If your results were unexpected, hypothesize why that might be the case

#### References

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Image test"}

ottrpal::include_slide("https://docs.google.com/presentation/d/1dI8-_iVqbkzNMf11M4dK85E8ZW3OyZECs_YwMKw5fhs/edit#slide=id.g362974128df_0_80")

```

All the references that you cite on your poster must be present in a References section including the following sections: Introduction, Methods, and Discussion. To save space on our posters, we will number our references (ex. 1-5) and use the numbers as citations throughout the text of your poster. You may have a lot of references; it is okay to put them in tiny text if you have to in order to make them fit.

There are many different ways to format the reference section. We will make ours in alphabetical order by the first author’s last name. All of your sources must be scientific journals and should use the following format:

> Authors (year) “Title.” Journal Name, vol. #, page #s, DOI

Online article that is also in print:

> Haussecker D., Huang Y., Lau A., Parameswaran P., Fire A. Z. and M. A. Kay (2010) “Human tRNA-derived small RNAs in the global regulation of RNA silencing.” RNA, Vol. 16, page 637-695,  doi:10.1261/rna.2000810

Online article only:

> Marianes, A. and A. C. Spradling (2013) “Physiological and stem cell compartmentalization within the Drosophila midgut.” eLife, doi:10.7554/eLife.00886
    
**Check your references section**:

- [ ] &nbsp;All in-text citations in the introduction are included in the references
- [ ] &nbsp;All in-text citations in the methods are included in the references
- [ ] &nbsp;All in-text citations in the discussion are included in the references
- [ ] &nbsp;All references are from scientific journals
- [ ] &nbsp;All text that requires an in-text citation has one

#### Acknowledgements

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Image test"}

ottrpal::include_slide("https://docs.google.com/presentation/d/1dI8-_iVqbkzNMf11M4dK85E8ZW3OyZECs_YwMKw5fhs/edit#slide=id.g362974128df_0_30")

```

The acknowledgements section is where you give thanks to the people, organizations, and institutions that have supported you in your research. If relevant, include the grant ID # of your funding source. Institutions and organizations that have contributed to your research - but you do not belong to - can be thanked here.

**Check your acknowledgements section:**

- [ ] &nbsp;Thank any funding source and the grant # are listed here
- [ ] &nbsp;Thank your research mentor (if applicable)
- [ ] &nbsp;Thank those who have provided you with technical support (if applicable)


### Part 3 - Proofread and Add Final Touches

*Estimated time: 30 min to an hour*

1. Each group member should re-read the poster from beginning to end and fix any typos or grammatical errors.
1. Check the alignment of figures, text boxes, titles, etc.
1. Add some finishing touches. You can play with the color, the font, add additional images if it’s relevant.

### Part 4 - Canvas Discussion

*Estimated time: 30 min*

You will turn in your poster to be graded as a group in a Canvas Assignment and post it to a Canvas Discussion to be viewed by the class.

1. Convert your poster to a pdf.
1. Have one member of your group turn in the pdf of your poster to the Graded Canvas Assignment. This assignment is already set up so that if one group member turns it in, it will show as submitted for all students in the group. This is where your instructor will grade you poster as a group.
1. Have one member of your group post a pdf of your poster in the Canvas C-MOOR Poster Discussion.
    a. With your poster, introduce your  group members and copy and paste your abstract into the post.
    a. Insert your pdf into the post and edit the link so that it automatically shows the inline preview. This will make it easier for students to view your poster.
1. As an individual, read through the other posters from different groups.
1. Post comments

### Grading Criteria

Everyone in the group earns the same grade, so it is important to work together.

| Points | Category |
|:-|:-|
| 2 points | Title, Authors and Affiliations |
| 3 points | Abstract |
| 4 points | Introduction <br> 2 - relevant background <br> 2 - drosophila as a model system |
| 5 points | Methods |
| 5 points | Results |
| 4 points | Discussion |
| 5 points | References ( 2 primary sources, 5 sources total) |
| 2 points | Poster Organization  |

### Footnotes

#### Resources

- [Google Doc]

#### Contributions and Affiliations

- Stephanie R. Coffman, Clovis Community College
- Valeriya Gaysinskaya, Johns Hopkins University
- Frederick Tan, Johns Hopkins University
- Sayumi York, Notre Dame of Maryland University

Last Revised: June 2025

## Activity - Share Your Poster

### Introduction

It's almost time!  Prepare for your final presentation by thinking about how to describe the great work that you've done this semester in both written and oral form.  Assume that your audience has a basic scientific background but does not know a lot about your particular field.  Provide enough context to give your listener a reason to care about your project and each of the results you will describe.  You have five minutes to get your story across so have a plan and practice.

#### Activity 1 – Share Your Poster

*Estimated time: 20 min*

#### Instructions

1. Download your poster as a .png file
- [https://drive.google.com/drive/folders/1y_GCJl7VIYTS_5y7057u2s58ZCdm_PxM](https://drive.google.com/drive/folders/1y_GCJl7VIYTS_5y7057u2s58ZCdm_PxM)

2. (One person on behalf of the group) Create a New Topic on the Discussion Forum with the title of your poster as the topic title and your .png file as the contents in either the

a. Look at This! category if every member of your group is ok sharing your work publicly
[https://help.c-moor.org/c/look-at-this/8](https://help.c-moor.org/c/look-at-this/8)

b. JHU 2025 Spring category if you need to keep your work private
https://help.c-moor.org/c/jhu-2025-spring/46

3. (Each person in the group) Reply to your topic using your own words with the following two bolded sections using the following template

|  |
|:--|
|**What I Did**|
|<Briefly describe what you did including what you found most interesting>|
|**How You Can Help**|
|<Briefly describe how others could continue this analysis especially what you would do next if you were to continue this project>|
<br>

#### Questions

| 1. Provide URL of your Discussion Forum post |
|:--|
||
<br>

### Activity 2 – Present Your Poster

*Estimated time: 40 min*

#### Instructions

1. Create a plan for a 5 min presentation taking into consideration

a. Who will speak when

b. What each person will cover

2. Practice your presentation

a. In your group

b. To the class


#### Questions

| Create a bullet point outline of who will speak what when: |
|:--|
|Overview (question, background, hypothesis)|
|Approach (dataset, general methods) |
| Results (detailed methods, notable results)|
|Conclusions (summary, next steps)|
<br>

### Grading Criteria

- Download as Microsoft Word (.docx) and upload on Canvas

### Footnotes

**Resources**

- [Google Doc]

**Contributions and Affiliations**

- Valeriya Gaysinskaya, Johns Hopkins University
- Frederick Tan, Johns Hopkins University

Last Revised: April 2025


# Next Steps

Now that you've finished your C-MOOR project, how do you close out your research experience or take it further? In this section we'll explore how to publicize and use your experience to help build your professional career.

## Lecture - Next Steps

*Estimated time: ---*

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Image test"}

ottrpal::include_slide("https://docs.google.com/presentation/d/1PMvZ19kSTK2ghdgLNFRS_t5p8R_GKFNbExPRxMsE1Ns/edit#slide=id.g35f391192_00")

```

[Slides: Next Steps](https://docs.google.com/presentation/d/1PMvZ19kSTK2ghdgLNFRS_t5p8R_GKFNbExPRxMsE1Ns/edit?usp=sharing)


## Update your CV

*Estimated time: 10 min*

Everyone who completes a C-MOOR project can add their experience to their resume or CV! We advise you and your students to do this as soon as possible after the end of class while your research project is still on your mind.

#### Resume or CV?

You may hear the terms resume and CV being used interchangeably. While both are drawn from the same information, they vary in brevity and focus.

A **resume** is a one-page (sometimes two-page) document of your experiences generally used for jobs outside of academia and research labs. It's not uncommon for people to have more than one resume, as it's best to tailor every resume to each specific role you're applying to.

A **Curriculum Vitae (CV)** is an extensive document that can take as many pages as needed to list the entirety of your research and academic experience. It often includes sections that aren't found in non-academic fields such as publications, conferences, and published papers. 

Most positions will detail which they require from applicants and most colleges and universities will be able to help you build either at your library or career center. We suggest that current students and recent graduates interested add their C-MOOR research experience to either their classwork or projects section. Remember to acknowledge the contributions of your team members if applicable; this does not count against you in your applications! Here are some examples of how you might word your experiences; notice how they're similar to an abstract in just one or two sentences:

- **An RNA-seq project:** Along with a partner, examined differential expression data of the *period (per)* gene along the *Drosophila melanogaster* midgut from a published dataset (Marianes & Spradling 2013) using DESeq2 and ClusterProfiler. We discovered an elevated expression of per in the anterior region of the midgut where the primary digestion and absorption of carbohydrates occur. Our results were presented as a research poster at the 2025 Kuntz Research Day symposium and have implications for using Drosophila as a model for the connection between the circadian rhythm and metabolic disorders.

- **A 16S project:** My group and I profiled the abundance of Archean ASVs in the gut microbiome from a published 16S study comparing the gut microbiota of people before, during, and after a standardized diet (Guthrie et al. 2022). As a part of this study, we created a PCoA and performed an alpha diversity analysis in phyloseq. Archean community members are often overlooked in microbiome studies; we found differential abundance in *Methanobacteria* between male and female participants regardless of diet and hypothesize this may be due to consumption of fiber reported by male subjects pre- and post-diet.

- **A WGS project**: Public data (SRA#######) from Robinson et al. (2021) was analyzed in Galaxy using Trimmomatic, Megahit, and Krona to determine the viral abundance in samples from tap water from various North American Lakes and make comparisons to lake depth. Viral abundance was correlated with geographic distance between samples; future studies could examine if this pattern persists in samples sourced from Europe and Oceana. 

Your blurb is a strong blurb when:

- [ ] &nbsp; You credit the source of your data (Citation, SRA #, Project #)
- [ ] &nbsp; You describe why your research project matters
- [ ] &nbsp; You list some of the computational platforms or software you used

**Q: Will people think I am an expert in genomics and bioinformatics if I put my project on my resume/CV? I don't want to look like a phony.**

A: As a current student or new graduate, you are not expected to have mastery over any scientific domain. What you are trying to show is you have taken an idea and brought it to completion, your ability to learn new concepts and skills, and your previous exposure to research. You can explain more about your role in the project in an interview.

**Q: Can I list things like R or Galaxy in my skills section?**

A: You can, however we suggest being explicit in your experience and add the level at which you feel comfortable with each respective platform. Are you R (Beginner) or R (Proficient)? Can you teach someone else how to do your project? Can you perform your project with novel data? How good are you at troubleshooting? This answer may seem contrary to the previous one, but remember that other people who are listing these platforms in their skills section includes computer/data scientists (majors) and bioinformaticians (majors), so people may assume mastery. Think about it the same way you would a foreign language. Spanish (Beginner) describes a different level of skill than 'just' Spanish. 

## C-MOOR Scholars

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Image test"}

ottrpal::include_slide("https://docs.google.com/presentation/d/1dI8-_iVqbkzNMf11M4dK85E8ZW3OyZECs_YwMKw5fhs/edit#slide=id.g362a06a915d_2_4")

```

C-MOOR Scholars are research clubs that function as an extension of the C-MOOR curriculum. You can explore techniques and concepts from modules you've yet to take to learn about different approaches we can use to explore different questions through genomics, connect with other scholars and mentors, and experience the climate of a research lab. 

**What C-MOOR Scholars is**:

  - A place to grow your skills
  - A place to network
  - A place to connect science with the greater community

**What C-MOOR Scholars is not**:

  - A commitment to pursuing research as a career
  - A graded class where we score work
  - A drop-in drop-out popular science club
  
Less formal than a class, more formal than just a gathering of like-minded minds, C-MOOR Scholars provides structure for your growth as a scientist. We are actively looking to recruit new scholars for chapters at our established sites (CCC, JHU, & NDMU); speak with your instructor for more information or reach out to us at the [C-MOOR Academy Discussion Forum](help.c-moor.org) to hear about any remote opportunities we have.

## Pursue further research

Perhaps you're interested in pursuing research beyond what C-MOOR currently provides. Maybe you're more interested in wet lab work, or a specific model organism. We encourage you to try all sorts of different opportunities even if you feel totally comfortable working with C-MOOR so you can better understand what kind of roles suit you best. This section serves as a guide for some common jumping off points to find outside research opportunities.

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Image test"}

ottrpal::include_slide("https://docs.google.com/presentation/d/1dI8-_iVqbkzNMf11M4dK85E8ZW3OyZECs_YwMKw5fhs/edit#slide=id.g362974128df_0_98")

```

### Research opportunities at your institution

Many colleges and universities have research programs for their students or resources available to connect you to some. You can ask your instructor, adviser, or library for more information. Some popular programs include:

- **Undergraduate Research Opportunity Programs (UROP):** Which often provide a database or pipeline of research opportunities for students at the univeristy or from surrounding areas. 

- **Research experiences for undergraduates (REU):** Similar to UROP, but generally open for a wider audience of students from outside the community. See the [NSF REU website](https://www.nsf.gov/funding/initiatives/reu) for more information.

Opportunities come and go and often follow the academic-year in terms of availability. If you can't find something immediately, keep trying!

### Find a research lab to join

You can choose to pursue additional research opportunities in what we consider the more traditional way: by reaching out to a professor or research scientist whose work you are interested in and asking if they might be willing to have you in their lab. As these opportunities are at the discretion of the lab leader they will vary widely in their scope, duration, and ability to provide financial support.

An email to a potential research lab should contain:

- [ ] An introduction about yourself (name, class year, institution, major)
- [ ] 1-2 sentences about your previous experience in research
- [ ] 1-2 sentences about why you're interested in their lab specifically
- [ ] A polite, open ended request to work with them

> Dear Professor Penguin,

>My name is Student, and I am a junior at My University majoring in biology (or other). I read your chapter on the genetics yellow-eyed penguins in Penguins: Natural history and conservation, and then checked out your profile on the University website. My interests are broadly defined in environmental toxicology and I am interested in the work you are doing using eDNA and studies on the effects of plastic on developing penguin transcriptomes.

>I previously completed a project as a part of an RNA-seq miniCURE and have some exposure to working with DESeq2, though I still have much to learn. My group and I profiled the gene expression of the genes XYZ in the Drosophila midugt and I presented our poster at our university's research day poster session.

>Thank you for your time and consideration in reading my email. Please let me know if you are currently available to mentor an undergraduate in your lab and if you would be willing to have me as a potential student. I hope to hear from you soon!

Don't be surprised if it takes the researcher a while to get back to you or if they respond curtly. They likely get many requests and are very busy. Continue to reach out to labs and apply to programs; it is difficult to know when opportunities are available as funding fluctuates.

## BioDIGS

This section is primarily geared toward instructors as students will be able to get access to the BioDIGS data through their local C-MOOR Scholars chapter.

```{r, fig.align='center', out.width="100%", echo = FALSE, fig.alt= "Image test"}

ottrpal::include_slide("https://docs.google.com/presentation/d/1dI8-_iVqbkzNMf11M4dK85E8ZW3OyZECs_YwMKw5fhs/edit#slide=id.g362a06a915d_2_10")

```


**What is BioDIGS?**: [BioDIGS](biodigs.org) is a project from the Genomic Data Science Community Network (GDSCN), which aims to characterize the microbiome of soil throughout sites in the US while connecting scientists to research. 

**What makes BioDIGS different?:** Soil is hypothesized to be the most diverse system on our planet, and BioDIGS is gathering sequence data and matching environmental data to elucidate the connection of soil microbes to abiotic variables and human health. Students at participating sites can take the entire project from soil sampling all the way through computational analysis. Curricula and more information on how to get a soil sampling kit are available on the BioDIGS website.















