```{r, include = FALSE}
ottrpal::set_knitr_image_path()
```

# Project Work Preparation

## Lecture: Possible Datasets

```{r, echo=FALSE, fig.alt=''}
ottrpal::include_slide("https://docs.google.com/presentation/d/1VxwSmAY8BUs3EfVcxPm3I8kNYJWjVqoHJrGOX3X3sog/edit?slide=id.g35f391192_00#slide=id.g35f391192_00")
```

[Slides: Possible Datasets](https://docs.google.com/presentation/d/1VxwSmAY8BUs3EfVcxPm3I8kNYJWjVqoHJrGOX3X3sog/edit?usp=sharing)


## Activity: Possible Datasets

### Activity

*Estimated time: 50 min*

#### Instructions

1. Skim three abstracts

2. Pick one and answer the following questions

a) Notice – What about this abstract most interests you?

b) Dataset – Summarize at a high level where the samples came from, how many there are, and what technology was used for sequencing.

c) Wonder – Two or three questions you would like to ask using this (and any other) datasets.

3. Post your answers by replying to the “Project Work: Possible Datasets” topic in the Discussion Forum

|Possible Datasets (Long-read PacBio)|
|:--|:--|:--|:--|
|**Soil**| | | |
| |Antarctic |PRJNA1126331 | https://pubmed.gov/39300163/| 
| |Biocrust |PRJNA691698 | https://pubmed.gov/34795375/| 
|**Water**| | | |
| |Fresh Water |PRJNA924152 | https://pubmed.gov/36823661/|
| |Ocean Water |PRJNA853328 | https://pubmed.gov/36448813/|
|**Human Gut**| | | |
| |Vegan/Omnivore |PRJNA750084 | http://pubmed.gov/36289209|
| |Infant Nutrition |PRJNA1139951 | http://pubmed.gov/31022095|
|**and More!**| | | |
| |Lamb Gut |PRJNA595610 |http://pubmed.gov/34980911|
| |Deadwood |PRJNA603240 | http://pubmed.gov/39627869|
| |Cheese |PRJNA778418 | http://pubmed.gov/9948695|
| |Whey |PRJNA454439, PRJNA477604 | http://pubmed.gov/6593500 |
<br>

### Grading Criteria

- <mark style="background color: yellow">Submit URL to your reply on Canvas

### Footnotes

**Contributions and Affiliations**

- Valeriya Gaysinskaya, Johns Hopkins University
- Frederick Tan, Johns Hopkins University

Last Revised: May 2022

# Kickstart Project Work

