```{r, include = FALSE}
ottrpal::set_knitr_image_path()
```

# SciServer Tutorials

## Meet R

### Introduction

R is a popular programming language for statistical computing and data visualization [wikipedia](https://wikipedia.org/wiki/R_(programming_language).  Notable features include the [RStudio IDE](https://posit.co/products/open-source/rstudio) built to help you be more productive with R (and Python); the [tidyverse](https://tidyverse.org/packages) collection of packages that aims to make data science faster, easier, and more fun; and importantly the [Bioconductor](https://bioconductor.org) project with its active support community and robust genomics tooling.  Now that you completed “test-driveR” and got a taste of analyzing a real world genomics dataset using R it’s time to learn more about how R stores and operates on data using concepts such as variables, vectors, and data.frames.

### Activity

*Estimated time: 25 min*

#### Instructions

1. Resume your C-MOOR LearnR container

  a. Open sciserver.org in a web browser and log in to your account.

  b. Click “Home” in the top menu to return to the home page.

  c. Scroll down to the second set of boxes and click “Compute”.

  d. Resume your C-MOOR LearnR container by clicking on its name.

2. Complete your next LearnR tutorial

  a. Click on “Meet R!”. The tutorial will open in a new tab.

  b. Complete the tutorial and answer the questions below.

#### Questions

|1. Variables – Define what is a variable, give a line of R code that stores information in a variable, and explain how one would view the data stored in a variable.|
|:--|
| Define variable:|
| Code:|
| Explain:|
<br>

|2. Vectors – Provide two lines of R code, one which stores a vector of numbers in a variable, and one which performs a mathematical operation on each element of that variable (e.g. multiplication). |
|:--|
|Code 1:|
|Code 2:|
<br>

|3. Plotting – Copy and paste as text your code from the final code block in the tutorial.  Also insert a screenshot of your resulting plot.|
|:--|
|Code text:|
|Plot screenshot:|
<br>

### Grading Criteria

- <mark style="background color: yellow">Download as Microsoft Word (.docx) and upload on Canvas

### Footnotes

**Resources**

- Google Doc
- [R cheat sheet](https://github.com/C-MOOR/cure-rnaseq/blob/master/tutorials/Rcheatsheet.md)

**Contributions and Affiliations**

- Katherine Cox, Johns Hopkins University
- Frederick Tan, Johns Hopkins University

Last Revised: February 2025


## R for Data Science 1 

### Introduction

[R for Data Science (2e)](https://r4ds.hadley.nz) covers how to do data science with R using the tidyverse collection of packages.  There are many possible reasons for the continued popularity of tidyverse, but one stand out principle the package authors embrace is that programs should be “easy to use by humans.  Computer efficiency is a secondary concern” (see this and more at the [tidy tools manifesto](https://tidyverse.tidyverse.org/articles/manifesto.html#design-for-humans0).  Here you will learn more about what kind of data can be organized into data.frames and possible ways to summarize, explore, and visualize datasets.

### Activity

*Estimated time: 50 min*

#### Instructions

1. Complete the “r4ds” LearnR tutorial.

- In addition to the “OCS – Global Diets” section being optional, you similarly do not need to complete all of the Exercises in 3.3.1.

2. Answer the questions below.

#### Questions

|1. data.frames – Data frames organize data into a 2-dimensional table of rows and columns like a spreadsheet with some special restrictions.  For the mpg data.frame, what do rows represent?  What do columns represent?|
|:--|
||
<br>


|2. Functions – Most R commands are functions (e.g. `mean()`) which take some input (a number, a vector, a dataframe...) and produce some output (a summary, a plot, a new vector...).  Describe one function you learned about that you anticipate being useful in the future.|
|:--|
||
<br>

|3. Common Problems – What are some common problems you ran into?  Refer to Part 2. Troubleshooting if you'd like some inspiration for how to put your experience into words.|
|:--|
||
<br>

|4. [*optional*] OCS - Global Diets Plotting – Which foods show a difference based on sex?|
|:--|
||
<br>

### Grading Criteria

- Download as Microsoft Word (.docx) and upload on Canvas

### Footnotes

**Resources**

- Google Doc
- [R cheat sheet](https://github.com/C-MOOR/cure-rnaseq/blob/master/tutorials/Rcheatsheet.md)

**Contributions and Affiliations**

- Katherine Cox, Johns Hopkins University
- Frederick Tan, Johns Hopkins University

Last Revised: February 2025


## test-driveR

### Introduction

SciServer [sciserver.org](https://www.sciserver.org) is an online platform for doing scientific data analysis. It is used by scientists studying astronomy, biology, oceanography, and more, and is free as long as you are using it for scientific research. Using SciServer means you do not need a fancy computer or need to install any special programs on your computer, you can just log in with your internet browser to start doing research. For this course, we have set up SciServer with customized collections of programs as well as the data that we’ll be analyzing. Once you sign up for SciServer and are added to the group for this course, you will be able to access these tools and begin your data analysis journey!

### Activity

*Estimated time: 25 min*

#### Instructions

1. Accept invitation to join class SciServer Group

a. Navigate to [https://apps.sciserver.org/dashboard/groups](https://apps.sciserver.org/dashboard/groups)

b. Click “Accept Invitation”

2. Start up a “C-MOOR LearnR” compute container

a. Navigate to [https://apps.sciserver.org/compute](https://apps.sciserver.org/compute)

b. Click “Create container”

c. Give your container a name (eg. my LearnR)

d. In the “Compute Image” drop-down menu, select “C-MOOR LearnR”

e. Under “Data Volumes”, check the box next to “C-MOOR Data”

```{r, echo=FALSE, fig.alt=''}
ottrpal::include_slide("https://docs.google.com/presentation/d/1hYKF7Ss3vJ8rrUIH7ByNh1BUlRa2fhsJhq8MXzEowCc/edit?slide=id.g35ea50429a3_0_9#slide=id.g35ea50429a3_0_9")
```
f. Scroll down and click “Create”. This may take a moment.

g. Start your C-MOOR LearnR container by clicking on its name

- NOTE: If you see “Error: C-MOOR data volume not mounted!” you most likely forgot to check the box next to “C-MOOR Data” when you created the container.

3. Complete your first LearnR tutorial

a. Click on “test-driveR”. The tutorial will open in a new tab.

```{r, echo=FALSE, fig.alt=''}
ottrpal::include_slide("https://docs.google.com/presentation/d/1hYKF7Ss3vJ8rrUIH7ByNh1BUlRa2fhsJhq8MXzEowCc/edit?slide=id.g35ea50429a3_0_27#slide=id.g35ea50429a3_0_27")
```
Complete the tutorial and answer the questions below.

#### Questions

Use the blocks provided at the end of the tutorial to create variations of the code provided in the first three exercises (Sort Data, Extract Data, and Plot Data). When you are done, submit the code and resulting output that you found most interesting. Briefly describe why you found it most interesting.

|1. Code – Copy and paste your actual code as text.|
|:--|
||
<br>

|2. Output – Copy and paste as text if simple, otherwise use a screenshot.|
|:--|
||
<br>

|3. Description.|
|:--|
||
<br>

### Grading Criteria

- <mark style="background color: yellow">Download as Microsoft Word (.docx) and upload on Canvas

### Footnotes

**Resources**

- Google Doc
- [R cheat sheet](https://github.com/C-MOOR/cure-rnaseq/blob/master/tutorials/Rcheatsheet.md)

**Contributions and Affiliations**

- Katherine Cox, Johns Hopkins University
- Frederick Tan, Johns Hopkins University

Last Revised: February 2025



## R for Data Science 2

### Introduction

[R for Data Science (2e)](https://r4ds.hadley.nz) describes the importance of data visualization by saying that “a good visualization will show you things you did not expect or raise new questions about the data”.  Here you will learn more about the [ggplot2](https://ggplot2.tidyverse.org) system for making graphs which is an elegant and versatile complement to what is available through software like Google Sheets.  Increasingly more software packages use the ggplot2 system such as the Bioconductor [phyloseq](https://bioconductor.org/packages/phyloseq) package used for 16S rDNA analysis.


### Activity

*Estimated time: 25 min*

#### Instructions

1. Start the “r4ds2” LearnR tutorial.

- Focus on the first half of the tutorial, up to and including “4. Structure of a ggplot() command”

2. Bug fixes

a. For the Chapter 3, Quiz 2 on geom_bar() aesthetics, you must check “size”

b. For the Chapter 4 exercises, you will need to add this code to the top of each code block


`measles <- filter(us_contagious_diseases, disease=="Measles")
measles_MD <- filter(measles, state=="Maryland")
measles_VA <- filter(measles, state=="Virginia")`

#### Questions

There are seven examples of broken ggplot code at the end of “4. Structure of a ggplot() command”.  Fix at least three of them and for one of them explain what was wrong and how you were able to figure it out.  Remember that you must add the above three lines to the top of each code block.

|1. What was the error?|
|:--|:--|
| |
<br>

|2. How did you figure it out?|
|:--|:--|
| |
<br>


### Grading Criteria

- <mark style="background color: yellow">Download as Microsoft Word (.docx) and upload on Canvas

### Footnotes

**Resources**

- Google Doc
- [R cheat sheet](https://github.com/C-MOOR/cure-rnaseq/blob/master/tutorials/Rcheatsheet.md)
- [ggplot2 cheat sheet](https://rstudio.github.io/cheatsheets/data-visualization.pdf)

**Contributions and Affiliations**

- Katherine Cox, Johns Hopkins University
- Frederick Tan, Johns Hopkins University

Last Revised: February 2025



